Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-03-23 MUSES_vs_BYOD_solutions.tex
Añadiendo nueva estructura bibliografía

\section{Acknowledgements}
This paper has been funded in part by European project MUSES (FP7-318508), along with Spanish National project TIN2011-28627-C04-02 (ANYSELF), and GENIL PYR-2014-17, awarded by the CEI-BioTIC UGR.

\bibliographystyle{elsarticle-num}

% Antonio - Poner la bibliografía en fichero .bib

\begin{thebibliography}{00}

%\bibitem{ids13}
%Sommestad T., Hunstad A.. \emph{Intrusion detection and the role of the system administrator.}, from Swedish Defence Research Agency (FOI), Linköping, Sweden, 2013.

%\bibitem{m2m12}
%NTT DOCOMO, \emph{DOCOMO to Launch Global M2M Platform}, in M2M Magazine, December 2012.
%http://www.machinetomachinemagazine.com/2012/12/05/docomo-to-launch-global-m2m-platform/.

%\bibitem{suites12}
%The Radicati Group Inc., report \emph{Microsoft Office 365 - Analysis and Forecast, 2012-2016}. June 2012.

\bibitem{Adams_Users05}
Adams, A. and Sasse, A.:
\newblock {\em Users are not the enemy}.
\newblock Security and Usability: Designing Systems That People Can Use.
  O\'Reilly Associations, 2005.

\bibitem{cost_adjustment_07}
Alfaro-Cid, E., Sharman, K. and Esparcia-Alcázar, A.I.:
\newblock A genetic programming approach for bankruptcy prediction using a
  highly unbalanced database.
\newblock In M.~Giacobini, editor, {\em Applications of Evolutionary
  Computing}, volume 4448 of {\em Lecture Notes in Computer Science}, pages
  169--178. Springer Berlin Heidelberg, 2007.

\bibitem{AzurriMDM}
Azurri Communications.
\newblock Icon Mobilise.
\newblock \url{http://www.azzurricommunications.com/~/media/Resources/Brochures/Media/icon_mobilise_brochure_online.ashx}

\bibitem{SecPolComp12}
Al-Omari, A., El-Gayar, O., Deokar, A., and Walters, J.: \emph{Security Policy Compliance: User Acceptance Perspective}. 45th Hawaii International
Conference on System Sciences (pp. 3317-3326). IEEE, 2012.

\bibitem{BYOD13}
Bacik, S.: \emph{Security Implications of Bring Your Own Device, IT Consumerization, and Managing User Choices}, in Information Security Management Handbook, Sixth Edition, Volume 7, pp. 133-142, 2013.

\bibitem{EAs_Back96}
Back, T.:
\newblock {\em Evolutionary algorithms in theory and practice}.
\newblock Oxford University Press, 1996.

\bibitem{MachineLearning_Bishop06}
Bishop, C.:
\newblock {\em Pattern recognition and Machine Learning}.
\newblock Springer, 2006.

\bibitem{Blackberry_tool}
Blackberry.
\newblock Blackberry balance.
\newblock \url{http://es.blackberry.com/business/software/blackberry-balance.html}

\bibitem{Blackphone}
Blackphone.
\newblock \url{https://www.blackphone.ch/}

\bibitem{SecPolComp10}
Bulgurcu, B., Cavusoglu, H., and Benbasat, I.: \emph{Information security policy compliance: an empirical study of rationality-based beliefs and information security awareness}. MIS Quarterly, 34(3), 523-548. 2010.

\bibitem{botnet_detection_clustering_09}
Chang, S. and Daniels, T.E.:
\newblock P2P botnet detection using behavior clustering \& statistical tests.
\newblock In {\em Proceedings of the 2nd ACM Workshop on Security and
  Artificial Intelligence}, AISec '09, pages 23--30, New York, NY, USA, 2009.
  ACM.

\bibitem{SecPol09}
Cresson Wood, C. and Lineman, D.: \emph{Information Security Policies Made Easy Version 11}. Information Shield, Inc. 2009.

\bibitem{inferring_policies_socialnetworks_09}
Danezis, G.:
\newblock Inferring privacy policies for social networking services.
\newblock In {\em Proceedings of the 2Nd ACM Workshop on Security and
  Artificial Intelligence}, AISec '09, pages 5--10, New York, NY, USA, 2009.
  ACM.

\bibitem{Good_tool}
Good's Technology.
\newblock BYOD Solution.
\newblock
  \url{http://www1.good.com/secure-mobility-solution/bring-your-own-device.html}

\bibitem{GAs_Goldberg89}
Goldberg, D.E.:
\newblock {\em Genetic Algorithms in search, optimization and machine
  learning}.
\newblock Addison Wesley, 1989.

\bibitem{FeatureSelection_Guyon03}
Guyon, I.,  and Elisseeff, A.:
\newblock An introduction to variable and feature selection.
\newblock {\em J. Mach. Learn. Res.}, 3:1157--1182, 2003.

\bibitem{PatternMining_Han07}
Han, J., Cheng, H., Xin, D., and Yan, X.:
\newblock Frequent pattern mining: Current status and future directions.
\newblock {\em Data Min. Knowl. Discov.}, 15(1):55--86, 2007.

\bibitem{SecPolPenalty09}
Herath, T., and Rao, H.R.: \emph{Protection motivation and deterrence: a framework for security policy compliance in organisations}. European Journal of Information Systems, vol. 18, pp. 106-125, 2009.

\bibitem{IBM_tool}
IBM.
\newblock Hosted mobile device security management.
\newblock
\url{http://www-935.ibm.com/services/us/en/it-services/managed-security-services-cloud-computing} \url{ -hosted-mobile-device-security-management.html}

\bibitem{Clustering_Jain99}
Jain, A.K., Murty, M.N., and Flynn, P.~J.:
\newblock Data clustering: A review.
\newblock {\em ACM Comput. Surv.}, 31(3):264--323, Sept. 1999.

\bibitem{imbalance_techniques_02}
Japkowicz, N. and Stephen, S.:
\newblock The class imbalance problem: A systematic study.
\newblock {\em Intell. Data Anal.}, 6(5):429--449, Oct. 2002.

\bibitem{ibm11}
Kao, I-L.: \emph{IBM Security Services. Securing mobile devices in the business environment}, IBM, 2011.

\bibitem{feature_selection_anomalies_08}
Kloft, M., Brefeld, U., D\"{u}essel, P., Gehl, C. and Laskov, P.:
\newblock Automatic feature selection for anomaly detection.
\newblock In {\em Proceedings of the 1st ACM Workshop on Workshop on AISec},
  AISec '08, pages 71--76, New York, NY, USA, 2008. ACM.

\bibitem{GP_Koza92}
Koza, J.~R.:
\newblock {\em Genetic Programming: On the programming of computers by means of
  natural selection}.
\newblock MIT Press, Cambridge, MA, 1992.

\bibitem{EAs_securitycosts-kirta} 
Kirta, T., and Kivimaab, J.: Optimizing it security costs by evolutionary algorithms. In C. Czosseck and K. Podins, editors, Conference on Cyber Con ict,pages 145-160, CCD COE Publications, 2010.

\bibitem{DataMining_Lee01}
Lee, S.J. and Siau, K.:
\newblock A review of data mining techniques.
\newblock {\em Industrial Management \& Data Systems}, 101(1):41--46, 2001.

\bibitem{user_classification_ml_13}
Leontjeva, A., Goldszmidt, M., Xie, Y., Yu, F. and Abadi, M.:
\newblock Early security classification of skype users via machine learning.
\newblock In {\em Proceedings of the 2013 ACM Workshop on Artificial
  Intelligence and Security}, AISec '13, pages 35--44, New York, NY, USA, 2013.
  ACM.

\bibitem{sec_policy_evolution_gp_08}
Lim, Y.T., Cheng, P.C., Rohatgi, P. and Clark, J.A.:
\newblock Mls security policy evolution with genetic programming.
\newblock In {\em Proceedings of the 10th Annual Conference on Genetic and
  Evolutionary Computation}, GECCO '08, pages 1571--1578, New York, NY, USA,
  2008. ACM.

\bibitem{MIT05}
Lippmann, R.P., Ingols, K.W., Scott, C., Piwowarski, K., Kratkiewicz, K.J., Artz, M., and Cunningham, R.K.: \emph{Evaluating and Strengthening Enterprise
Network Security Using Attack Graphs}. Project Report IA-2. Lincoln Laboratory, Massachusetts Institute of Technology, October 2005.

\bibitem{GP_intrusion-lu} Lu, W. and Traore, L.: Detecting new forms of network intrusion using genetic programming. In Proceedings of the 2003 Congress on Evolutionary Computation, pages 2165-2172, 2003.

\bibitem{EventProcessing_Luckham02}
Luckham, D.:
\newblock {\em The Power of Events: An Introduction to Complex Event Processing
  in Distributed Enterprise Systems}.
\newblock Addison-Wesley, MA, USA, 2002.

\bibitem{classification_67}
MacQueen, J.:
\newblock Some methods for classification and analysis of multivariate
  observations.
\newblock In {\em Proceedings of the fifth Berkeley symposium on mathematical
  statistics and probability}, volume~1, page~14. California, USA, 1967.

\bibitem{GA_intrusion-majeed} Majeed, P.G. and Kumar, S. Genetic algorithms in intrusion detection systems: A survey. International Journal of Innovation and Applied Studies, 5(3):233-240, March 2014.

\bibitem{Opp_Security11}
Oppliger, R.:
\newblock Security and privacy in an online world.
\newblock {\em IEEE Computer}, 44(9):21--22, September 2011.

\bibitem{android11}
Orthacker, C., Teufl, P., Kraxberger, S., Lackner, G., Gissing, M., Marsalek, A., Leibetseder, J., and Prevenhueber, O.: \emph{Android Security Permissions - Can We Trust Them?}. MobiSec Session on Smartphone Security, Aalborg 2011.

\bibitem{BigData_11}
Ratner, B.:
\newblock {\em Statistical and Machine-Learning Data Mining: Techniques for
  Better Predictive Modeling and Analysis of Big Data, Second Edition}.
\newblock CRC Press, Inc., Boca Raton, FL, USA, 2nd edition, 2011.

\bibitem{policy_generation_clustering_10}
Samak, T. and Al-Shaer, E.:
\newblock Synthetic security policy generation via network traffic clustering.
\newblock In {\em Proceedings of the 3rd ACM Workshop on Artificial
  Intelligence and Security}, AISec '10, pages 45--53, New York, NY, USA, 2010.
  ACM.

\bibitem{Samsung_tool}
Samsung KNOX.
\newblock
  \url{https://www.samsungknox.com}

\bibitem{Schu_SecPatterns05}
Schumacher, M., Fernandez-Buglioni, E., Hybertson, D., Buschmann, F., and
  Sommerlad, P.:
\newblock {\em Security Patterns: Integrating Security and Systems
  Engineering}.
\newblock John Wiley \& sons, 2005.

\bibitem{RT2AE_SOTICS13}
Seigneur, J.-M., Kölndorfer, P., Busch, M., and Hochleitner, C.:
\newblock A survey of trust and risk metrics for a BYOD mobile working world.
\newblock In {\em Third International Conference on Social Eco-Informatics
  (SOTICS 2013)}, page To Appear. Curran Associates Inc., November 2013.

\bibitem{SecPolComp09}
Shaw, R.S., Chen, C.C., Harris, A.L., and Huang, H.-J.: \emph{The impact of information richness on information security 
awareness training effectiveness}. Computers \& Education, vol. 52, pp. 92-100, 2009.

\bibitem{SecPolComp07}
Siponen, M., Pahnila, S., and Mahmood, A.: \emph{Employees' adherence to information security policies: an empirical study}. In IFIP International Federation for Information Processing, Volume 232, New Approaches for Security, Privacy and Trust in Complex Environments pp. 133-144, 2007.

\bibitem{AAI_book_2009}
Solanas, A. and Martínez-bal, A.:
\newblock {\em Advances in Artificial Intelligence for Privacy Protection and
  Security}.
\newblock World Scientific Publishing Co., Inc., River Edge, NJ, USA, 2009.

\bibitem{Sophos_tool}
Sophos.
\newblock Mobile control.
\newblock \url{http://www.sophos.com/en-us/products/mobile-control.aspx}

\bibitem{rule_generation_gp_09}
Suarez-Tangil, G., Palomar, E. Fuentes, J., Blasco, J. and Ribagorda, A.:
\newblock Automatic rule generation based on genetic programming for event
  correlation.
\newblock In l.~Herrero, P.~Gastaldo, R.~Zunino, and E.~Corchado, editors, {\em
  Computational Intelligence in Security for Information Systems}, volume~63 of
  {\em Advances in Intelligent and Soft Computing}, pages 127--134. Springer
  Berlin Heidelberg, 2009.

\bibitem{risk_reduction_ga_12}
Tamjidyamcholo, A.:
\newblock Genetic algorithm approach for risk reduction of information
  security.
\newblock {\em International Journal of Cyber-Security and Digital Forensics
  (IJCSDF)}, 1(1), 2012.

\bibitem{SurveyEventCorrelation_Tiffany02}
Tiffany, M.:
\newblock A survey of event correlation techniques and related topics.
\newblock Research paper, Georgia Institute of Technology, 2002.

\bibitem{WorxSDK}
Citrix.
\newblock Worx App SDK.
\newblock \url{http://www.citrix.es/go/worx-app-sdk.html}

\bibitem{WSO2_tool}
WSO2.
\newblock Enterprise Mobility Manager.
\newblock \url{http://wso2.com/products/enterprise-mobility-manager/}

\bibitem{GA_networksecurity-zarza} 
Zarza, L., Forné, J., Pegueroles, J.R., and Soriano, M.: Advances in artificial intelligence for privacy protection and security, chapter Genetic algorithms for designing network security protocols, pages 325-358. World Scientific, 2010.

\bibitem{GA_cryptographicprotocols-zarza2} 
Zarza, L., Pegueroles, J., Soriano, M., and Martínez, R.: Design of cryptographic protocols by means of genetic algorithms techniques. In M. Malek, E. Fernández-Medina, and J. Hernando, editors, SECRYPT, pages 316-319. INSTICC Press, 2006.

\end{thebibliography}

\end{document}

>>>>

\section{Acknowledgements}
This paper has been funded in part by European project MUSES
(FP7-318508), along with Spanish National projects
TIN2011-28627-C04-02
(ANYSELF) and TIN2014-56494-C4-3-P (EphemeCH), and GENIL PYR-2014-17,
awarded by the CEI-BioTIC UGR.

\bibliographystyle{elsarticle-num}
\bibliography{geneura-latin1,review_muses}

\end{document}
%%% Local Variables:
%%% ispell-local-dictionary: "english"
%%% hunspell-local-dictionary: "english"
%%% End:
